An Improved ANS Transaction Template

### 2018-01-27 paper.tex
comment nomenclature
commenting apendix
conclusion draft + Acknowledgments

Where the JCPOA aggrement

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Appendix}

Numbering in the appendix is different:
\begin{equation} \label{eq:appendix}
  2 + 2 = 5\,.
\end{equation}
and another equation:
\begin{equation} \label{eq:appendix2}
  a + b = c\,.
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Nomenclature}

\begin{table}[H]
    \centering
    \begin{tabular}{l|l}
%         &  \\
        $N$ & Feed assay \\
        $N'$ & Product assay \\
        $N''$ & Tails assay \\
        $\alpha$ & Feed to product enrichment factor \\
        $\beta$ & Feed to tail enrichment factor \\
        $\theta$ & Cut
    \end{tabular}
%    \caption{Caption}
    \label{tab:my_label}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
This material is based upon work supported a Department of Energy Nuclear
Energy University Programs Graduate Fellowship.

>>>>

The JCPOA aggrement limits to 5060 runing centrifuges in the Natanz Fuel
Enrichment Plant (NFEP) so about $10\%$ of its design capacity, the reference
case allows to build $1$ SQ of HEU in 8 months (versus in 24 days without the JCPOA
agrement limitations). While using directly the 5060 centrifuges to produce 1 SQ
of HEU take about 8 months, case 1 and the case 2 will produce it in 2 years.
Nevertheless the diversion scenario from case 1 or 2 will be hard if not
impossible to detect from the cascasde configuration.

While the results of this work might be limited, it aims to develop a
methodology to study diversion scenarios, from the fuel cycle perspective.
Futhermore, additional methods to compute the CascadeEnrich response to
non-ideal feed assay will be investigated.  The CascadeEnrich facility used will
also be improved in order to take advantage of the dynamical flow managment of
the Cyclus framework, allowing for example to automatically assign the cascade
to the different level as the need evolve.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \appendix
%% \section{Appendix}
%% 
%% Numbering in the appendix is different:
%% \begin{equation} \label{eq:appendix}
%%   2 + 2 = 5\,.
%% \end{equation}
%% and another equation:
%% \begin{equation} \label{eq:appendix2}
%%   a + b = c\,.
%% \end{equation}
%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \section{Nomenclature}
%%
%% \begin{table}[H]
%%     \centering
%%     \begin{tabular}{l|l}
%% %         &  \\
%%         $N$ & Feed assay \\
%%         $N'$ & Product assay \\
%%         $N''$ & Tails assay \\
%%         $\alpha$ & Feed to product enrichment factor \\
%%         $\beta$ & Feed to tail enrichment factor \\
%%         $\theta$ & Cut
%%     \end{tabular}
%% %    \caption{Caption}
%%     \label{tab:my_label}
%% \end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments} 
This work was funded by the Consortium for Verification Technology under
Department of Energy National Nuclear Security Administration award number
DE-NA0002534
